How One Microtask Affects Another

### 2016-01-03 docs/publications/2015.12_CHI/man.tex
add revised CHI manuscript

\begin{abstract}
Microtask platforms are becoming commonplace tools for performing human
research, producing gold-standard data, and annotating large datasets.
These platforms connect \textit{requesters}
(researchers or companies) with large populations (crowds) of workers, who 
perform small tasks, typically taking less than five minutes each.
A topic of ongoing research concerns the design of tasks that elicit high
quality annotations.
Here we identify a seemingly banal feature of nearly all crowdsourcing 
workflows that profoundly impacts workers' responses.
Microtask assignments typically consist of a sequence 
of tasks sharing a common format (e.g., circle galaxies in an image). 
Using image-labeling, a canonical microtask format, we 
discover that earlier tasks have a priming effect on the worker, shifting 
the distribution of future responses by 30-50\% 
(total variational distance). 
Specifically, prior tasks influence the content that workers focus on, 
as well as the richness and specialization of responses. 
We call this phenomenon \textit{intertask effects}.
We compare intertask effects to the overt framing, 
effected by stating the requester's research interest, 
and find that intertask effects are on par or stronger.
While intertask effects can be a source of systematic bias, 
our results suggest that, with appropriate task design, 
they might be leveraged to hone worker focus and acuity, 
helping to elicit reproducible, expert-level judgments.
Intertask effects are a crucial aspect of human computation that should be
considered in the design of any crowdsourced study.
\end{abstract}

@@

Psychological experiments show that the exposure to stimuli immediately 
before performing a task influences performance, an effect known as 
\textit{priming} \cite{BJOP1796}.
The effect of priming appears to be stronger when the modality of the
prime is the same as the task.
Thus, the typical microtask setup creates conditions in which
earlier tasks could induce bias in later ones, through priming.

We seek to determine if any significant priming effect occurs between
tasks, and if so, to measure and characterize it.
Certain tasks admit a well-defined notion of ``correct'' and 
``incorrect'' responses.  But many tasks involving qualitative judgment
do not.  Rather than simply characterizing effects on accuracy, we seek
to provide a generalized measure of bias, by quantifying the
extent to which intertask effects can shift the distribution of responses 
to a task.  
Measuring the \textit{extent} of the shift in response distribution,
i.e. the extent of bias, is substantially harder than
simply determining \textit{whether} a biasing effect has occurred.  
Our first contribution is a statistically grounded method for doing so.

To investigate the phenomenon in a
highly generalizable setting, we sought a task that would involve 
qualitative judgment and enable relatively unconstrained responses. 
We also sought a task that would be a typical exemplar of the kinds of
tasks actually seen on microtask platforms (see 
Table~\ref{table:task_composition} for examples).  For this purpose, we 
adopted
image-labeling as a canonical microtask, in which workers provide 
descriptive labels to images using free-text inputs.  Image labeling is
a qualitative task without clearly ``correct'' or ``incorrect'' responses,
and is among the most common kinds of tasks on the major crowdsourcing
platform Amazon's Mechanical Turk (see Table \ref{table:task_composition}).  If task-induced priming arises in our 
setup, it should be expected in an overwhelming number of microtasks and 
crowdsourced workflows where workers are called upon to provide qualitative
judgment.

@@

Our results show that a worker's responses are strongly influenced by 
the content of tasks performed beforehand, leading to as much as 50\%
bias (measured as total variational distance, 
see Figure~\ref{fig:l1_example} for illustrative definition).  
Using the WordNet 
knowledge base, we analyze worker's word choices to characterize 
the nature of these effects in detail.  We find that, when workers 
label a series of images that are more similar, their responses become 
more specialized and more diverse.  
Prior tasks can shift the topical focus of 
worker's labels, inducing them to focus on different aspects of the images.

As a point of comparison, we perform similar experiments, in which we
alter the framing of microtask assignments, in terms of the stated purpose
of the task, or by naming the funder.
Remarkably, the effects of prior microtasks themselves,
which are virtually ubiquitous, are on par with, or stronger than, 
overtly framing an assignment.

We call the effects that earlier tasks exert on later ones 
\textit{intertask effects}.  If, as has been suggested \cite{5543192}, 
microtask platforms are to be considered as a new form of computing 
architecture, it will be necessary to reconcile the fact that the human 
computing elements exhibit \textit{hysteresis}, 
meaning that microtask workers' outputs 
depend on the \textit{history} of their inputs.
We propose a dual priming mechanism which can explain our
observations.  Irrespective of the underlying mechanism, this 
very strong effect might be exploited in task design to tune worker 
focus and acuity.

As our main contributions, we
\begin{itemize}[noitemsep,nolistsep]
  \item{derive a general method for measuring bias in responses;}
  \item{measure bias in microtasks due to prior tasks;}
  \item{show this effect is stronger than, or on par with framing;}
  \item{
	show that when completing a series of similar microtasks,
	worker's responses become more specialized and diverse;
  }
\end{itemize}

The rest of the paper is organized as follows.  In the next section, we 
review the relevant prior work.  We then present a method for 
measuring bias due to intertask effects.  
Next we present our experimental results, followed by a discussion 
of interpretations and ramifications for microtask-based and crowdsourced 
work.  We conclude with suggestions for task design and future work.

@@

\begin{table}
\centering
\begin{tabular}{l c c}
\toprule
Task Type & Count & Fraction (\%) \\
\toprule
Image transcription & 57 & 28.5 \\
Information gathering & 46 & 23.0 \\
Image tagging and classification & 36 & 18.0 \\
Copy writing and editing & 18 & 9.0 \\
Text tagging and classification & 15 & 7.5 \\
Audio/Video transcription & 12 & 6.0 \\
Survey & 9 & 4.5 \\
Unknown & 7 & 3.5 \\
\bottomrule
\end{tabular}
\caption{
	Frequency of various broad task types seen among the 200 most 
	recently posted tasks on Amazon's Mechanical Turk, 
	accessed on 12 February, 2015.
}
\label{table:task_composition}
\end{table}

@@

\section{Measuring the extent of priming}
If a prior task acts as a prime for a later one, 
and thereby introduces bias, the bias will manifest as
a shift in the distribution of responses 
workers provide for the later task.
A variety of tests exist to determine \textit{whether} two samples, 
i.e. sets of responses, come from different distributions, 
most notably the $\chi^2$ test.  
This will suffice to determine whether there are any grounds for concern 
about priming effects in the first place.  However, such tests
do not tell us \textit{how much} two distributions differ, and hence
how severe the priming effects are.

Determining the severity of priming effects amounts to measuring a 
distance, or \textit{divergence}, between response distributions, by
sampling responses from workers exposed to different priming conditions.
We will present a method for bounding a kind of divergence known as 
\textit{total variational distance}\footnote{
  Other formulations such as the Kullback-Leibler and 
  Jensen-Shannon divergence can be calculated from the total variational
  distance.
}, which we will henceforth denote by $\theta$.
The value of $\theta$ between two distributions $P$ and $Q$ 
is the fraction under the graph of $P$ that does not overlap with that
under $Q$ (or vice-versa; see Figure~\ref{fig:l1_example}).  
Formally:
\begin{align}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p(x) - q(x) \right|,
	\label{eq:theta}
\end{align}
Where $p(x)$ and $q(x)$ are the respective probabilities 
that a worker submits response $x$, from a set of possible responses 
$\mathcal{X}$, under distributions $P$ and $Q$.
The divergence is constrained to 
$0 \leq \theta \leq 1$ (or from 0 to 100\%).
When $\theta = 100\%$, the distributions do not overlap at all.  
When $\theta = 0\%$, the distributions are identical.
For reference, the distributions plotted in 
Figure~\ref{fig:l1_example}A and B have $\theta=50\%$ and $\theta=30\%$ 
respectively.

@@

Empirically measuring the divergence between distributions
is a matter of ongoing
research \cite{val-thesis,batu2013testing,chan2014optimal}.
In the ``na\"ive'' approach one first uses the samples to reconstruct 
empirical
distributions, by calculating their maximum likelihood parameters.
Then, one substitutes the empirical values of $p(x)$ and $q(x)$ into 
Equation~\ref{eq:theta} \cite{batu2013testing}.  
For example, one might directly estimate $\hat{p}(x) = N_x/N$, 
where $N_x$ is the number of times response $x$ is observed among $N$ 
total responses.

However this approach can \textit{drastically} overestimate $\theta$
\cite{val-thesis}.  As an illustrative example,
suppose that we have sampled two sets of 1000 words from \textit{possibly} 
different distributions, and that we wish to estimate the divergence 
between these distributions.  
It turns out that, if both sets of words were actually drawn from 
an identical Zipf distribution\footnote{The 
  Zipf distribution is a common model for word frequencies 
  \cite{powers1998applications,zipf1949human}:
  \begin{align}
	p(x) = \frac{x^{-1}}{\sum_{n=1}^{\infty}x^{-1}},
	\label{eq:zipf}
  \end{align}
  where $p(x)$ is the probability of the $x$th most common word.
}, the na\"ive approach would typically lead one to report 
$\hat{\theta} \approx 65\%$, even though, in reality $\theta = 0\%$
(this can be shown by simulated sampling).

@@

\section{Results}
\begin{figure}
	\includegraphics[scale=0.36]{figs/task-schematic-2.pdf}
	\caption{
	  Template for the experiments described in the main text.
	  After selecting our assignment on Mechanical 
	  Turk, workers were separated into two treatments.
	  Workers from each treatment were subjected to framing and/or
	  five initial tasks, which differed between treatments, and then 
	  completed a set of five test tasks that were identical for both
	  treatments.  Most experiments involved either framing or initial
	  tasks (see table \ref{table:experiments}), 
	  but \textit{frame-food-culture} involved both.
	  After the experiment, workers return to the Mechanical Turk 
	  task-selection interface.
	}
	\label{fig:task-schematic}
\end{figure}

@@

\begin{figure}[t]
	\includegraphics[scale=0.75]{figs/theta.pdf}
	\caption{
		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
		classifier, induced in image-labeling tasks, due to workers' 
		exposure to framing and prior tasks.  
		(\textbf{A}) Exposing workers to initial tasks induced more severe
		bias than framing, except when echoed framing was used. 
		(\textbf{B}) As workers proceeded through test tasks, 
		the bias due to initial tasks waned, 
		but remained significant even after five tasks.  
		Standard error bars are shown.
	}
	\label{fig:theta}
\end{figure}

We performed a series of five experiments
on Amazon's Mechanical Turk using 1071 workers.  
Every experiment consisted of two treatments, each with 119 workers,
who performed a single assignment\footnote{Workers could not participate 
multiple times in our study.}\textsuperscript{,}\footnote{On Mechanical Turk, individual 
assignments are called Human Intelligence Tasks (HITs), but this use of 
``task'' is 
different from our current one: in our experiment each HIT actually 
involves 10 image-labeling tasks.}.  
The setup in each experiment followed the template depicted in 
Figure~\ref{fig:task-schematic}.  
The assignments had two parts.  The first part of the assignment differed
between the two treatments, and consisted of a set of initial tasks 
and/or framing (by describing the purpose of the assignment or source of 
funding).  In the second part of the assignment, workers from both
treatments completed the same five \textit{test tasks}.  Each of the 
initial and test tasks required workers to provide five descriptive labels
for an image.  The tasks were performed one at a time,
and, in treatments involving both initial and test tasks, there was no
interruption or distinction made between the initial and test tasks from
the perspective of the worker.

We analyzed the
workers' responses to the test tasks to determine whether
they were influenced by the initial tasks (or framing).  We looked for 
differences in the distributions of test responses 
using a $\chi^2$ test.  We then measured the 
severity of bias induced by initial tasks and framing, by 
constructing a na\"ive Bayes classifier to infer the workers' 
treatments based on their responses to test tasks, 
and measuring its accuracy.

\begin{table}[b!]
\small
\centering
\setlength{\tabcolsep}{1pt}
\begin{tabular}{c c c c c}
\toprule
Experiment & \parbox[c]{3.0cm}{\centering{Priming modality}} & Initial Tasks & Frame \\
\midrule
\multirow{2}{*}{\textit{intertask-food-objects}} 
& \multirow{2}{*}{initial tasks} & \textit{food} & none \\
  & & \textit{objects} & none  \\

\noalign{\smallskip}
\hdashline
\noalign{\smallskip}

\multirow{2}{*}{\textit{frame-food-objects}} 
& \multirow{2}{*}{framing} & none 
	& ``food''\textsuperscript{a} \\
& & none 
	& ``objects''\textsuperscript{b} \\

\noalign{\smallskip}
\hdashline
\noalign{\smallskip}

\multirow{2}{*}{\textit{echo-food-objects}} 
& \multirow{2}{*}{echoed framing} & none
	& ``food''\textsuperscript{c} \\
& & none & ``objects''\textsuperscript{d} \\

\noalign{\smallskip}
\hdashline
\noalign{\smallskip}

\multirow{2}{*}{\textit{intertask-food-culture}} 
& \multirow{2}{*}{initial tasks} & \textit{food} 
	& none \\
& & \textit{culture} 
	& none \\

\noalign{\smallskip}
\hdashline
\noalign{\smallskip}

\multirow{2}{*}{\textit{frame-food-culture}} 
& \multirow{2}{*}{framing} & \textit{food} 
	& ``food''\textsuperscript{e} \\
  & & \textit{food}
	& ``culture''\textsuperscript{f} \\

\bottomrule
\end{tabular}
\caption{
	Description of experiments performed.  Each experiment had two treatments
	which differed either in the initial tasks shown or the framing used 
	(the priming modality).  
	During echoed framing, the worker had to respond to the framing language
	using a combo box input.  The framing language used was as follows:
	\newline\textsuperscript{a} ``Funded by the laboratory for the visual 
		perception of Food and Ingredients''
	\newline\textsuperscript{b} ``Funded by the laboratory for the visual 
		perception of Objects and Tools''
	\newline\textsuperscript{c} ``The purpose of this study is to understand the visual perception of Food and Ingredients''
	\newline\textsuperscript{d} ``The purpose of this study is to understand the visual perception of Objects and Tools''
	\newline\textsuperscript{e} ``This research is proudly funded by The National 
		Foundation for Nutritional Awareness''
	\newline\textsuperscript{f} ``This research is proudly funded by The Global 
		Foundation for the Recognition of Cultures''
}
\label{table:experiments}
\end{table}

{\bf Existence of inter-task effects.} In our first experiment called \textit{intertask-food-objects},
workers were assigned to either a \textit{food} or \textit{objects} 
treatment.  Workers from these treatments performed initial tasks 
in which they labeled, respectively, 
images depicting either food or (non-food) objects
(see example images in Figure~\ref{fig:task}A and B).  
Workers from both treatments then performed five test tasks, which
contained images
depicting both food and objects (Figure~\ref{fig:task}C).

The frequencies of words used by
workers in the \textit{food} and \textit{objects} treatments differed
significantly during test tasks ($p = 6.0 \times 10^{-14}$),
even though the test tasks were identical in both treatments.  
Thus earlier tasks do significantly affect later ones, which 
validates our concerns about the typical microtask methodology.

The heterogeneity of word-frequencies between treatments was based on 
Pearson's $\chi^2$ test with Yates' correction.
In linguistics applications, the use of a $\chi^2$ to test for 
heterogeneity between corpora has been called
into question, because there is frequently heterogeneity \textit{within}
a given corpus \cite{kilgarriff1996comparing}.
This occurs because certain documents in a corpus will regard certain 
topics, leading to bursty word usage.  While our setup is substantially
remote from the applications for which this concern was raised, 
one could argue that the responses to a given treatment
constitute a ``corpus'', and the responses of a given worker to a 
``document''.
To address this concern, we randomly split responses to given treatment
into two sets, and tested for hetererogeneity between the sets.
In all cases, we failed to find heterogeneity \textit{within} a given 
treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
Thus, the heterogeneity we observed \textit{between} treatments is 
meaningful.

{\bf Strength of inter-task effects.} Having affirmed the \textit{existence} of intertask effects, we sought to
measure the severity of the bias induced, i.e. $\theta$.
To measure $\theta$ we used a na\"ive Bayes classifier based on a 
multinomial distribution over the word frequencies in worker's labels, 
and measured it's accuracy using leave-one-out cross-validation.  
We chose the na\"ive Bayes
classifier for three reasons.  First, it performs well even when the 
number of features is large compared to the number of training examples
\cite{bickel2004,hastie2009elements}.  
Second, there are no hyperparameters to 
optimize, which eliminates the need to partition the response data into
dev and test sets.
Third, the conditional independence assumption, normally 
undertaken for pragmatic reasons \cite{Zhang2004562}, 
is probably a relatively mild in 
relation to image labels, since they are likely to be less dependent
on one another than in a coherent passage of text.  We repeated our
analysis used a support vector machine and found very similar results.

@@

Based on the classifier accuracy, intertask effects in the 
experiment \textit{intertask-food-objects}
lead to (a lower bound) bias of $\theta=30.6\%$ between workers from the 
\textit{food} and \textit{objects} treatments (Figure~\ref{fig:theta}A).
It is difficult to visualize the distributions of word frequencies,
but for reference, the distributions shown in 
Figure~\ref{fig:l1_example}B have $\theta = 30\%$.  This represents a 
substantial potential to distort microtask results.

@@

As already discussed, there has been considerable interest in the 
effects that framing can have on microtask responses
\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, and 
framing effects are arguably similar to inter-task effects in the sense 
that both arise from the worker's experiences immediately before 
performing a task.
Therefore, as a point of comparison, we performed a similar experiment 
in which we suggested the focus of the study by stating a name for
the requester within the task.
In the experiment 
\textit{frame-food-objects}, we used the same test tasks as in 
\textit{intertask-food-objects}, but the initial tasks were omitted, 
and in their stead, workers were either told that the study was 
``Funded by the laboratory for the 
visual perception of Food and Ingredients'', 
or ``\ldots of Objects and Tools''.

Framing induced changes in the frequencies of 
word usage at significance 
(as determined by $\chi^2$ test; $p=0.0012$).  But, 
the \textit{extent} of framing-induced bias was not statistically 
distinguishable from zero ($p =0.37$) (Figure~\ref{fig:theta}A).
And so, remarkably, the extent of bias due to framing was weaker than that 
due to intertask effects ($p=2.1\times 10^{-5}$)\footnote{To compare bias
  due to framing and inter-task effects, we approximated the distribution
  of correct classifications as a normal distribution, and performed
a (two-tailed) two-proportion $z$-test.}.
In other words, the \textit{microtasks themselves}
had a stronger biasing effect than framing.

>>>>

\begin{abstract}
Microtask platforms are becoming commonplace tools for performing human
research, producing gold-standard data, and annotating large datasets.
These platforms connect \textit{requesters}
(researchers or companies) with large populations (crowds) of workers, who 
perform small tasks, typically taking less than five minutes each.
A topic of ongoing research concerns the design of tasks that elicit high
quality annotations.
Here we identify a seemingly banal feature of nearly all crowdsourcing 
workflows that profoundly impacts workers' responses.
Microtask assignments typically consist of a sequence 
of tasks sharing a common format (e.g., circle galaxies in an image). 
Using image-labeling, a canonical microtask format, we 
discover that earlier tasks have a priming effect on the worker, shifting 
the distribution of future responses by 30-50\% 
(total variational distance). 
Specifically, prior tasks influence the content that workers focus on, 
as well as the richness and specialization of responses. 
We call this phenomenon \textit{intertask effects}.
We compare intertask effects to the overt framing, 
effected by stating the requester's research interest, 
and find that intertask effects are on par or stronger.
If uncontrolled, intertask effects could be a source of systematic bias, 
but our results suggest that, with appropriate task design, 
they might be leveraged to hone worker focus and acuity, 
helping to elicit reproducible, expert-level judgments.
Intertask effects are a crucial aspect of human computation that should be
considered in the design of any crowdsourced study.
\end{abstract}

@@

Psychological experiments show that the exposure to stimuli immediately 
before performing a task influences performance, an effect known as 
\textit{priming} \cite{BJOP1796}.
The effect of priming appears to be stronger when the modality of the
prime is the same as the task.
Thus, the typical microtask setup creates conditions in which
the contents of earlier tasks could influence responses to later ones.

We seek to determine if any such effects in fact occur and if so, 
to measure and characterize them.
Certain tasks admit a well-defined notion of ``correct'' and 
``incorrect'' responses.  But many tasks involving qualitative judgment
do not.  Rather than simply characterizing effects on accuracy, we seek
to provide a generalized measure of the extent to which prior tasks
can alter the distribution of responses to a task.  
Measuring the \textit{extent} of the shift in response distribution, is 
substantially harder than simply determining \textit{whether} an effect 
has occurred.  Our first contribution is a statistically grounded method 
for doing so.

To investigate the phenomenon in a
highly generalizable setting, we sought a task that would involve 
qualitative judgment and enable relatively unconstrained responses. 
We also sought a task that would be a typical exemplar of the kinds of
tasks actually seen on microtask platforms (see 
Table~\ref{table:task_composition} for examples).  For this purpose, we 
adopted
image-labeling as a canonical microtask, in which workers provide 
descriptive labels to images using free-text inputs.  Image labeling is
a qualitative task without clearly ``correct'' or ``incorrect'' responses,
and is among the most common kinds of tasks on the major crowdsourcing
platform Amazon's Mechanical Turk (see Table \ref{table:task_composition}).
If task-induced priming arises in our 
setup, it could be expected in a large number of microtasks and 
crowdsourced workflows where workers are called upon to provide qualitative
judgment.

@@

Our results show that a worker's responses are strongly influenced by 
the content of tasks performed beforehand, leading to as much as 50\%
total variational distance (see Figure~\ref{fig:l1_example} for 
illustrative definition of total variational distance).  
Using the WordNet 
knowledge base, we analyze worker's word choices to characterize 
the nature of these effects in detail.  We find that, when workers 
label a series of images that are more similar, their responses become 
more specialized and more diverse.  
Prior tasks can shift the topical focus of 
worker's labels, inducing them to focus on different aspects of the images.

As a point of comparison, our experiments included framing treatments, 
in which we altered the framing of microtask assignments, in terms of the 
stated purpose of the task, or by naming the funder.
Remarkably, the effects of prior microtasks themselves,
which are virtually ubiquitous, are on par with, or stronger than, 
overtly framing an assignment.

We call the effects that earlier tasks exert on later ones 
\textit{intertask effects}.  If, as has been suggested \cite{5543192}, 
microtask platforms are to be considered as a new form of computing 
architecture, it will be necessary to reconcile the fact that the human 
computing elements exhibit \textit{hysteresis}, 
meaning that microtask workers' outputs 
depend on the \textit{history} of their inputs.

Unraveling the psychological mechanisms that give rise to such strong 
effects will require further investigation.  We describe a possible 
mechanism based on positive and negative priming, consistent with the
observations from our experiments.
Irrespective of the underlying mechanism, this very strong effect might 
be exploited in task design to tune worker focus and acuity.

As our main contributions, we
\begin{itemize}[noitemsep,nolistsep]
  \item{
	derive a method for measuring changes in response distributions;
  }
  \item{measure the influence of initial microtasks on later ones;}
  \item{show this effect is stronger than, or on par with framing;}
  \item{
	show that when completing a series of similar microtasks,
	worker's responses become more specialized and diverse;
  }
\end{itemize}

The rest of the paper is organized as follows.  In the next section, we 
review the relevant prior work.  We then present our method for 
measuring changes to response distributions.
Next we present our experimental results, followed by a discussion 
of interpretations and ramifications for microtask-based and crowdsourced 
work.  We conclude with suggestions for task design and future work.

@@

\begin{table}
\centering
\begin{tabular}{l c c}
\toprule
Task Type & Count & Fraction (\%) \\
\toprule
Image transcription & 57 & 28.5 \\
Information gathering & 46 & 23.0 \\
Image labeling and classification & 36 & 18.0 \\
Copy writing and editing & 18 & 9.0 \\
Text tagging and classification & 15 & 7.5 \\
Audio/Video transcription & 12 & 6.0 \\
Survey & 9 & 4.5 \\
Unknown & 7 & 3.5 \\
\bottomrule
\end{tabular}
\caption{
	Frequency of various broad task types seen among the 200 most 
	recently posted tasks on Amazon's Mechanical Turk, 
	accessed on 12 February, 2015.
}
\label{table:task_composition}
\end{table}

@@

\section{Measuring changes to response distributions}
When a prior task influences a later one, this influence will manifest as
a shift in the distribution of responses workers provide for the later 
task.
A variety of tests exist to determine \textit{whether} two samples, 
i.e. sets of responses, come from different distributions, 
most notably the $\chi^2$ test.  
However, such tests
do not tell us \textit{how much} two distributions differ, and hence
how strongly the initial task's influence is.

Determining the strength of intertask effects amounts to measuring a 
distance, or \textit{divergence}, between response distributions.
We will present a method for bounding a kind of divergence known as 
\textit{total variational distance}\footnote{
  Other formulations such as the Kullback-Leibler and 
  Jensen-Shannon divergence can be calculated from the total variational
  distance.
}, which we will henceforth denote by $\theta$.
The value of $\theta$ between two distributions $P$ and $Q$ 
is the fraction under the graph of $P$ that does not overlap with that
under $Q$ (or vice-versa; see Figure~\ref{fig:l1_example}).  
Formally:
\begin{align}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p(x) - q(x) \right|,
	\label{eq:theta}
\end{align}
Where $p(x)$ and $q(x)$ are the respective probabilities 
that a worker submits response $x$, from a set of possible responses 
$\mathcal{X}$, under distributions $P$ and $Q$.
The divergence is constrained to 
$0 \leq \theta \leq 1$ (or from 0 to 100\%).
When $\theta = 100\%$, the distributions do not overlap at all.  
When $\theta = 0\%$, the distributions are identical.
For reference, the distributions plotted in 
Figure~\ref{fig:l1_example}A and B have $\theta=50\%$ and $\theta=30\%$ 
respectively.

@@

Empirically measuring the divergence between distributions
is a matter of ongoing
research \cite{val-thesis,batu2013testing,chan2014optimal}.
In the ``naive'' approach one first uses the samples to reconstruct 
empirical
distributions, by calculating their maximum likelihood parameters.
Then, one substitutes the empirical values of $p(x)$ and $q(x)$ into 
Equation~\ref{eq:theta} \cite{batu2013testing}.  
For example, one might directly estimate $\hat{p}(x) = N_x/N$, 
where $N_x$ is the number of times response $x$ is observed among $N$ 
total responses.

However this approach can \textit{drastically} overestimate $\theta$
\cite{val-thesis}.  As an illustrative example,
suppose that we have sampled two sets of 1000 words from \textit{possibly} 
different distributions, and that we wish to estimate the divergence 
between these distributions.  
It turns out that, if both sets of words were actually drawn from 
an identical Zipf distribution\footnote{The 
  Zipf distribution is a common model for word frequencies 
  \cite{powers1998applications,zipf1949human}:
  \begin{align}
	p(x) = \frac{x^{-1}}{\sum_{n=1}^{\infty}x^{-1}},
	\label{eq:zipf}
  \end{align}
  where $p(x)$ is the probability of the $x$th most common word.
}, the naive approach would typically lead one to report 
$\hat{\theta} \approx 65\%$, even though, in reality $\theta = 0\%$
(this can be shown by simulated sampling).

@@

\section{Experiment 1}
\subsection{Setup}
%\begin{figure}
%	\includegraphics[scale=0.36]{figs/task-schematic-2.pdf}
%	\caption{
%	  Template for the experiments described in the main text.
%	  After selecting our assignment on Mechanical 
%	  Turk, workers were separated into two treatments.
%	  Workers from each treatment were subjected to framing and/or
%	  five initial tasks, which differed between treatments, and then 
%	  completed a set of five test tasks that were identical for both
%	  treatments.  Most experiments involved either framing or initial
%	  tasks (see table \ref{table:experiments}), 
%	  but \textit{frame-food-culture} involved both.
%	  After the experiment, workers return to the Mechanical Turk 
%	  task-selection interface.
%	}
%	\label{fig:task-schematic}
%\end{figure}

@@

\begin{figure}[t]
	\includegraphics[scale=0.75]{figs/theta.pdf}
	\caption{
		Empirical bias, $\theta_\mathrm{NB}$, measured using a naive Bayes 
		classifier, induced in image-labeling tasks, due to workers' 
		exposure to framing and prior tasks.  
		(\textbf{A}) Exposing workers to initial tasks induced more severe
		bias than framing, except when echoed framing was used. 
		(\textbf{B}) As workers proceeded through test tasks, 
		the bias due to initial tasks waned, 
		but remained significant even after five tasks.  
		Standard error bars are shown.
	}
	\label{fig:theta}
\end{figure}

The first experiment we performed consisted of two sub-experiments which
we will call ``intertask'' and ``framing'', because they are respectively
designed to measure intertask and framing effects.  The experiment was 
performed on Amazon's Mechanical Turk (MTurk) using 476 workers.  Workers
could only participate once in a given experiment, and could only 
participate in one of the experiments we present here.

The experiment was conducted using a single HIT\footnote{
  On MTurk, a HIT (or Human Intelligence Task) is the smallest 
  assignable unit of work.  The use of ``Task'' in HIT differs from that
  used here; here labeling a single image is considered to be one ``task'',
  and so a HIT is actually composed of 10 tasks.
}.  Workers who accepted the HIT were randomly assigned to one of the two
sub-experiments.  Both sub-experiments consisted of two treatments, which
we call ``food'' and ``culture'', and workers were also randomly 
assigned to a treatment.  In both treatments of both sub-experiments,
workers were asked to perform ten image-labeling tasks, each of which 
required the worker to assign five descriptive labels to an image.  
In all cases, the last five tasks were 
identical, and were presented in the same order.  
These last five tasks constituted the ``test tasks'', whose distribution
of responses could admit intertask or framing effects.

In the intertask sub-experiment, we varied the first five tasks given to 
workers based on the treatment.  Workers assigned to the ``food'' 
treatment were shown images of food, while workers assigned to the 
``culture'' treatment were shown other kinds of cultural depictions, such
as dance, sport, and music\footnote{We do not assert that cultural 
practices can be cleanly separated into food-related and non-food related 
ones; that is not necessary for our analysis.}.  
However, within a given treatment, workers were shown the same images in
the same order.  As mentioned, workers 
from both treatments then performed the same five test tasks.  The test
tasks consisted of images depicting meals of diverse ethnic origin.
From the perspective of the worker, there was no distinction between the 
initial and test tasks.

In the framing sub-experiment, we did not vary the initial tasks, but 
instead, introduced a \textit{framing slide} before the tasks.  
Depending on the treatment, the framing slide read 
``This research is proudly funded by The National Foundation for 
Nutritional Awareness'', or ``\ldots by the Global Foundation for the 
Recognition of Cultures''.  The intention here was to frame the task by
providing the name of a (fictitious) funder, and using names that
invite the worker to focus on different aspects of the image content.  
As already mentioned, the test tasks consisted of images depicting meals 
of diverse ethnic origin.

\subsection{Results}

\paragraph{Existence of intertask and framing effects.} 
Looking at the frequencies with which workers use words, we tested for
heterogeneity between the two treatments of each sub-experiment.
For the intertask sub-experiment, we found the distribution of responses 
for the two treatments differed significantly ($p=?$), 
demonstrating that intertask effects do exist.  However, we did not find 
significant effects due to framing, however (by $\chi^2$ test, $p=0.29$) 
(Figure~\ref{fig:theta}A).

Testing for heterogeneity of word-frequencies was based on 
Pearson's $\chi^2$ test with Yates' correction.
In linguistics applications, the use of a $\chi^2$ to test for 
heterogeneity between corpora has been called
into question, because there is frequently heterogeneity \textit{within}
a given corpus \cite{kilgarriff1996comparing}.
This occurs because certain documents in a corpus will regard certain 
topics, leading to bursty word usage.  While our setup is substantially
remote from the applications for which this concern was raised, 
one could argue that the responses to a given treatment
constitute a ``corpus'', and the responses of a given worker to a 
``document''.
To address this concern, we randomly split responses to given treatment
into two sets, and tested for hetererogeneity between the sets.
In all cases, we failed to find heterogeneity \textit{within} a given 
treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
These results hold for Experiment 2 as well, to be discussed later.
Thus, the heterogeneity we observed \textit{between} treatments is 
meaningful.

\paragraph{Strength of intertask and framing effects.}
Having affirmed the \textit{existence} of intertask effects, we sought to
measure the strength of the effect, i.e. $\theta$.
To measure $\theta$ we created a naive Bayes classifier based on a 
multinomial distribution over the word frequencies in worker's labels, 
and measured it's accuracy using leave-one-out cross-validation.  
We chose the naive Bayes
classifier for three reasons.  First, it performs well even when the 
number of features is large compared to the number of training examples
\cite{bickel2004,hastie2009elements}.  
Second, there are no hyperparameters to 
optimize, which eliminates the need to partition the response data into
dev and test sets.
Third, the conditional independence assumption, normally 
undertaken for pragmatic reasons \cite{Zhang2004562}, 
is probably a mild in 
relation to image labels, since they are likely to be less dependent
on one another than in a coherent passage of text.  We repeated our
analysis using a support vector machine and found very similar results.

@@

Based on the performance of the classifier, intertask effects generated
51.3\% total variational distance (Figure~\ref{fig:theta}A).  
Visualy comparing two word frequency distributions is difficult, but 
Figure~\ref{fig:l1_example} provides an example of distributions having 
$\theta = 50\%$.  In contrast to intertask effects, the effect due to 
framing, was not significantly different from zero 
(Figure~\ref{fig:theta}A).
And so, the effect framing was weaker than that due to prior tasks 
($p=7.6\times 10^{-7}$)\footnote{To compare bias
  due to framing and intertask effects, we approximated the distribution
  of correct classifications as a normal distribution, and performed
a (two-tailed) two-proportion $z$-test.}.
In other words, the \textit{microtasks themselves}
had a stronger effect than framing.

@@

The results from the first experiment clearly show that intertask effects 
arise and are strong.  On the other hand, we were scarcely able to observe
any effect due to framing.  This raises a few questions which we seek
to answer using a second experiment.  The first question is simply whether
the result will replicate using different sets of images.  
If they do, then the next question is how intertask effects evolve
as the worker performs tasks.  Presumbaly, intertask effects wear off at 
some point, but is it after one task, two, or more?

Using the results from Experiment 1, 
we could look at the intertask effects for individual test questions, 
however, each question uses a distinct image, whose own content may
modulate the extent to which it can be influenced by intertask effects.
We cannot disentangle the question of task proximity from image content
in the results for Experiment 1.

In setting up Experiment 2, we also wish to increase the strength of 
framing.  While finding that intertask effects were stronger than framing 
was surprising and remarkable, perhaps the most meaningful comparison
would be one which shows just how extreme framing treatments need to be 
to produce effects on par with intertask effects.  
One factor that may have weakened the effects of framing in Experiment 1 
is the inclusion of initial tasks between the framing slide and the test 
tasks. They were included to ensure that workers had always completed the
same number of tasks before begining the test tasks.  However, their 
inclusion gives time for differential framing effects to 
subside, while also generating intertask effects that are 
\textit{shared} between the treatments, potentially masking the framing 
effects that remain.  In the next experiment, we measure framing effects 
immediately after onset of framing.

\section{Experiment 2}
\subsection{Setup}
In Experiment 2 we again have ``intertask'' and ``framing'' 
sub-experiments, but we include a third sub-experiment, ``echo'', which 
incorporates more extreme framing treatments.  
As before, each sub-experiment has
two treatments, but this time they are ``food'' and ``objects''.
Keeping a food treatment enables us to perform deeper lexical analysis of 
both experiments (discussed in the results for Experiment 2).  
The experiment was again performed using a single HIT on MTurk, 
and involved 1666 workers.
Workers were randomly assigned to a sub-experiment and treatment upon
starting the HIT.
